Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2021-03-28 rebuttal/ijcai21-authors-response.tex
one more comment

%-Is Figure 1 for the synthetic data? Please specify. Same question for Tables 2 and 3. In Figure 2, are the m=N,n=N lines the synthetic data?
%-Why is Figure 2 shown for only Pessimistic, not all the approaches? Were all approaches tested on all data sets? Or were all approaches only tested on synthetic data?
Yes, when we do not specify the name of the dataset we mean data generated following the procedure described in Sec 5. Regarding the real datasets, we only tested the Pessimistic strategy for the following reasons: $1)$ Random was considered only as a baseline in the first experiment, which shows that Pessimistic performs much better; $2)$ As pointed out in Sec 4, Extended Pessimistic is too computationally costly to run on larger instances; $3)$ Elitist was designed with the only purpose of challenging our best strategy (Pessimistic) in extreme cases tailored to favor the former. Testing this strategy in other settings does not yield interesting information; $4)$ Two Phases was designed to compare our interleaving approach to a more classical linear method. We thought that the most challenging situation (Impartial Culture) was the best setting to perform this test. \commentOC{What does the last sentence answer?}\commentBN{To why we didn't test Two Phases with real datasets.}

>>>>

%-Is Figure 1 for the synthetic data? Please specify. Same question for Tables 2 and 3. In Figure 2, are the m=N,n=N lines the synthetic data?
%-Why is Figure 2 shown for only Pessimistic, not all the approaches? Were all approaches tested on all data sets? Or were all approaches only tested on synthetic data?
Yes, when we do not specify the name of the dataset we mean data generated following the procedure described in Sec 5. Regarding the real datasets, we only tested the Pessimistic strategy for the following reasons: $1)$ Random was considered only as a baseline in the first experiment, which shows that Pessimistic performs much better; $2)$ As pointed out in Sec 4, Extended Pessimistic is too computationally costly to run on larger instances; \commentBN{I would keep the old phrasing to keep the same structure for all points (Extended Pessimistic ... as pointed out)} $3)$ Elitist was designed with the only purpose of challenging our best strategy (Pessimistic) in extreme cases tailored to favor the former. Testing this strategy in other settings does not yield interesting information; $4)$ Two Phases was designed to compare our interleaving approach to a more classical linear method. We thought that the most challenging situation (Impartial Culture) was the best setting to perform this test. \commentOC{What does the last sentence answer?}\commentBN{To why we didn't test Two Phases with real datasets.}
